---
title: "dv project review"
author: "19BCE1437 - B. Yeshaswini, 19BCE1667 - Baalamurgan KA"
date: "22/02/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(biglm)
library(broom)
library(reshape2)
library(RColorBrewer)
library(corrgram)
library(sigr)

library(e1071)
library(caTools)
library(class)
library(rmeta)
library(TTR)
library(tidyverse)
library(fpp)
library(forecast)
library(backtest)
library(quantmod)
library(lubridate)
```

```{r}
mydata <- read.csv("C:\\Users\\Yeshaswini\\OneDrive\\Desktop\\College\\sem 6\\DATA VISUALIZATION\\MALE.csv")
mydata <- na.omit(mydata)
mydata1 <- read.csv("C:\\Users\\Yeshaswini\\OneDrive\\Desktop\\College\\sem 6\\DATA VISUALIZATION\\FEMALE.csv")
mydata1 <- na.omit(mydata1)

colnames(mydata)[colnames(mydata) %in% c("X1991", "X1992","X1993", "X1994","X1995", "X1996","X1997", "X1998","X1999", "X2000","X2001", "X2002","X2003","X2004", "X2005","X2006","X2007", "X2008","X2009","X2010", "X2011","X2012","X2013","X2014","X2015","X2016","X2017","X2018","X2019")] <- c("1991", "1992","1993","1994","1995","1996","1997","1998","1999","2000","2001","2002","2003","2004","2005","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015","2016","2017","2018","2019")

head(mydata)

colnames(mydata1)[colnames(mydata1) %in% c("X1991", "X1992","X1993", "X1994","X1995", "X1996","X1997", "X1998","X1999", "X2000","X2001", "X2002","X2003","X2004", "X2005","X2006","X2007", "X2008","X2009","X2010", "X2011","X2012","X2013","X2014","X2015","X2016","X2017","X2018","X2019")] <- c("1991", "1992","1993","1994","1995","1996","1997","1998","1999","2000","2001","2002","2003","2004","2005","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015","2016","2017","2018","2019")
```


##BASIC STRUCTURES OF DATA
```{r}
str(mydata)
dim(mydata)
summary(mydata)
```


##BASIC EXPLORATION OF DATA
```{r}
##Working on TOP 5 countries
Code = "SGP"
particularcountry <- filter(mydata,Country.Code == Code)
#%>% summarise_if(is.numeric, mean)

particularcountryplot <- gather(particularcountry, key="Year", value="Unemployment_Rate",c(3:ncol(particularcountry))) 

head(particularcountryplot)



ggplot(particularcountryplot,aes(x=Year, y=Unemployment_Rate))+
  geom_col(stat='identity', fill="dark red")+
  scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+
   labs(title="Country wise unemployment rate distribution")


  
heatmap(as.matrix(mydata[3:7]))
image(as.matrix(mydata[3:8]))



plot(mydata[3:7],col=brewer.pal(3,"Set1"))
```


```{r}
#MALE
mydataplot <- gather(mydata, key="Year", value="Unemployent.rate",c(3:ncol(mydata)))
write.csv(mydataplot,"C:\\Users\\Yeshaswini\\Documents\\maledataplot.csv",row.names=FALSE)
head(mydataplot)

#FEMALE
mydataplot1 <- gather(mydata1, key="Year", value="Unemployent.rate",c(3:ncol(mydata1)))
write.csv(mydataplot1,"C:\\Users\\Yeshaswini\\Documents\\femaledataplot.csv",row.names=FALSE)
head(mydataplot1)
```


```{r}
#MALE
#Considering top 20 countries for Unemployment rate
lastcountries <- mydataplot %>% arrange(desc(Unemployent.rate))
lastcountries <- unique(lastcountries$ï..Country.Name)
lastcountriesnames <- lastcountries[20:length(lastcountries)]

#Removing the countries except top 20 countries
top20unemploymentdata_male <- mydataplot%>%select("ï..Country.Name","Year","Unemployent.rate")
for (countrypos in 1:length(lastcountriesnames)) {
  countrycheck = lastcountriesnames[countrypos]
  top20unemploymentdata_male <- top20unemploymentdata_male[!(top20unemploymentdata_male$ï..Country.Name == countrycheck[1]),]
}
head(top20unemploymentdata_male)
```

```{r}
#FEMALE
#Considering top 20 countries for Unemployment rate
lastcountries <- mydataplot1 %>% arrange(desc(Unemployent.rate))
lastcountries <- unique(lastcountries$ï..Country.Name)
lastcountriesnames <- lastcountries[20:length(lastcountries)]

#Removing the countries except top 20 countries
top20unemploymentdata_female <- mydataplot1%>%select("ï..Country.Name","Year","Unemployent.rate")
for (countrypos in 1:length(lastcountriesnames)) {
  countrycheck = lastcountriesnames[countrypos]
  top20unemploymentdata_female <- top20unemploymentdata_female[!(top20unemploymentdata_female$ï..Country.Name == countrycheck[1]),]
}
head(top20unemploymentdata_female)

ggplot(top20unemploymentdata_male, aes(x=Year, y=Unemployent.rate)) +
  geom_bar(stat='identity',color = "pink", fill="yellow") +
  facet_wrap(~ï..Country.Name)+
  labs(title = paste("Unemployment rate from 1991 - 2017 across top 20 countries"))
```


```{r}
##Unemployment rate in 1991 vs 2019
unemploymentdatacompareyearwise_female <- top20unemploymentdata_male
unemploymentdatacompareyearwise_female <- unemploymentdatacompareyearwise_female %>% filter(grepl('1991|2019', Year))

ggplot(unemploymentdatacompareyearwise_female, aes(x = ï..Country.Name, y = Unemployent.rate,label = Year)) +
    geom_point(aes(color = factor(Year)))+
    geom_text(hjust = 0, nudge_x = 0.05,check_overlap = TRUE)+
    scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+
    theme(axis.text.x = element_text(angle = 45, hjust=1))+
    labs(title = paste("Comparison of unemployment rate across top 20 countries in 1991 vs 2019."))
```
```{r}
ggplot(top20unemploymentdata_female, aes(x=Year, y=Unemployent.rate)) +
  geom_bar(stat='identity',color = "pink", fill="yellow") +
  facet_wrap(~ï..Country.Name)+
  labs(title = paste("Unemployment rate from 1991 - 2017 across top 20 countries"))

##Unemployment rate in 1991 vs 2019
unemploymentdatacompareyearwise_male <- top20unemploymentdata_female
unemploymentdatacompareyearwise_male <- unemploymentdatacompareyearwise_male %>% filter(grepl('1991|2019', Year))

ggplot(unemploymentdatacompareyearwise_male, aes(x = ï..Country.Name, y = Unemployent.rate,label = Year)) +
    geom_point(aes(color = factor(Year)))+
    geom_text(hjust = 0, nudge_x = 0.05,check_overlap = TRUE)+
    scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+
    theme(axis.text.x = element_text(angle = 45, hjust=1))+
    labs(title = paste("Comparison of unemployment rate across top 20 countries in 1991 vs 2019."))
```


```{r}
male <- read.csv("C:\\Users\\Yeshaswini\\Documents\\maledataplot.csv")
View(male)

female <- read.csv("C:\\Users\\Yeshaswini\\Documents\\femaledataplot.csv")
View(female)
plot(male$Year, male$Unemployent.rate,type = "l", main="Unemployment",xlab="Year", ylab="Unemployment rate" )
plot(female$Year, female$Unemployent.rate,type = "l", main="Unemployment",xlab="Year", ylab="Unemployment rate" )
```

```{r}
#Distribution of all Deaths in India
Code="IND"
indiadata <- male[(male$Country.Code==Code),]
indiadata <- indiadata[(indiadata$Year=="2019"),]

row.names(indiadata) <- indiadata$Year
indiadata <- indiadata[-1:-3]
indiadata <- indiadata[-3]
indiadata <- gather(indiadata, key="Deaths", value="Rate",c(1:ncol(indiadata)))
```


```{r}
fmla <- female$Unemployent.rate ~ male$Unemployent.rate
unemployment_model <- lm(fmla, data = mydataplot)
unemployment_model
```

## Coeffecients and F
### Call summary() on unemployment_model to get more details

```{r}
summary(unemployment_model)
glance(unemployment_model)
wrapFTest(unemployment_model)
summary(female)
summary(male)

```

## Prediction new data
### Predict female and male unemployment in the unemployment data set
```{r}
mydataplot$prediction <- predict(unemployment_model)
female$prediction <- predict(unemployment_model)
male$prediction <- predict(unemployment_model)
## female
ggplot(female, aes(x = prediction, y = Unemployent.rate)) + geom_point() + geom_abline(color = 'blue')

## male
ggplot(male, aes(x = prediction, y = Unemployent.rate)) + geom_point() + geom_abline(color = 'blue')

```


## prediction rate for female dataset
```{r}
newrates <- data.frame(male = 5)
newrates
newdata <- female
pred <- predict(unemployment_model, newdata = female)
predict(unemployment_model, newdata)
```


## prediction rate for male dataset
```{r}
newrates <- data.frame(male = 5)
newrates
newdata <- male
pred <- predict(unemployment_model, newdata = male)
predict(unemployment_model, newdata)
```


```{r}
print(fe_mean <- mean(unemployment_model$female_unemployment))
```

# KNN - FEMALE
```{r}
ts_pdata <- data.frame(female$Unemployent.rate,male$Unemployent.rate)
ts_pdata

set.seed(1234)
# Splitting data into train
# and test data
split <- sample.split(ts_pdata, SplitRatio = 0.7)
train_cl <- subset(ts_pdata, split == "TRUE")
test_cl <- subset(ts_pdata, split == "TRUE")
train_cl
# Feature Scaling
train_scale <- scale(train_cl[, 1, drop = TRUE])
test_scale <- scale(test_cl[, 1, drop = TRUE])
test_scale
train_scale
# Fitting KNN Model 
# to training dataset

classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$male.Unemployent.rate,
                      k = 2)
classifier_knn
```

```{r}
# Confusion Matrix
cm <- table(test_cl$male.Unemployent.rate, classifier_knn)
cm
  
# Model Evaluation - Choosing K
# Calculate out of Sample error
misClassError <- mean(classifier_knn != test_cl$male.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
  
# K = 3
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$male.Unemployent.rate,
                      k = 3)
misClassError <- mean(classifier_knn != test_cl$male.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
  
# K = 5
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$male.Unemployent.rate,
                      k = 5)
misClassError <- mean(classifier_knn != test_cl$male.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
  
# K = 7
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$male.Unemployent.rate,
                      k = 7)
misClassError <- mean(classifier_knn != test_cl$male.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
  
# K = 15
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$male.Unemployent.rate,
                      k = 15)
misClassError <- mean(classifier_knn != test_cl$male.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
  
# K = 19
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$male.Unemployent.rate,
                      k = 19)
misClassError <- mean(classifier_knn != test_cl$male.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
```

# KNN-Female

```{r}
ts_pdata <- data.frame(female$Unemployent.rate,male$Unemployent.rate)
ts_pdata

set.seed(1234)
# Splitting data into train
# and test data
split <- sample.split(ts_pdata, SplitRatio = 0.7)
train_cl <- subset(ts_pdata, split == "TRUE")
test_cl <- subset(ts_pdata, split == "TRUE")
train_cl
# Feature Scaling
train_scale <- scale(train_cl[, 1, drop = TRUE])
test_scale <- scale(test_cl[, 1, drop = TRUE])
test_scale
train_scale
# Fitting KNN Model 
# to training dataset

classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$female.Unemployent.rate,
                      k = 2)
classifier_knn

# Confusion Matrix
cm <- table(test_cl$female.Unemployent.rate, classifier_knn)
cm
  
# Model Evaluation - Choosing K
# Calculate out of Sample error
misClassError <- mean(classifier_knn != test_cl$female.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
  
# K = 3
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$female.Unemployent.rate,
                      k = 3)
misClassError <- mean(classifier_knn != test_cl$female.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
  
# K = 5
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$female.Unemployent.rate,
                      k = 5)
misClassError <- mean(classifier_knn != test_cl$female.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
  
# K = 7
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$female.Unemployent.rate,
                      k = 7)
misClassError <- mean(classifier_knn != test_cl$female.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
  
# K = 15
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$female.Unemployent.rate,
                      k = 15)
misClassError <- mean(classifier_knn != test_cl$female.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
  
# K = 19
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$female.Unemployent.rate,
                      k = 19)
misClassError <- mean(classifier_knn != test_cl$female.Unemployent.rate)
print(paste('Accuracy =', 1-misClassError))
```

# Time series Forecast - MALE
```{r}
male_ts <- aggregate(cbind(Unemployent.rate) ~ Year, data = male, sum)
ts_pdata <- data.frame(male_ts$Year,male_ts$Unemployent.rate)
ts_pdata

dt = sort(sample(nrow(ts_pdata), nrow(ts_pdata)*.7))
dat_train<-ts_pdata[dt,]
dat_test<-ts_pdata[-dt,]
dat_train
 
nrow(dat_train); nrow(dat_test)
data_ts <- ts(dat_train[, 2], start = c(min(male$Year),1), end = c(max(male$Year), 1), frequency = 1)
 
#lines 2 to 4 to find error(tells accuracy)
mape <- function(actual,pred){
  mape <- mean(abs((actual - pred)/actual))*100
  return (mape)
}

naive_mod <- naive(data_ts, h = 12)
summary(naive_mod)
plot(data_ts)
```

# Time series Forecast - FEMALE
```{r}
female_ts <- aggregate(cbind(Unemployent.rate) ~ Year, data = female, sum)
ts_pdata <- data.frame(female_ts$Year,female_ts$Unemployent.rate)
ts_pdata

dt = sort(sample(nrow(ts_pdata), nrow(ts_pdata)*.7))
dat_train<-ts_pdata[dt,]
dat_test<-ts_pdata[-dt,]
dat_train
 
nrow(dat_train); nrow(dat_test)
dat_ts <- ts(dat_train[, 2], start = c(min(male$Year),1), end = c(max(male$Year), 1), frequency = 1)
 
#lines 2 to 4 to find error(tells accuracy)
mape <- function(actual,pred){
  mape <- mean(abs((actual - pred)/actual))*100
  return (mape)
}

naive_mod <- naive(dat_ts, h = 12)
summary(naive_mod)
plot(dat_ts)
```
